Ribosome accumulation during early phase resistance training

### 2020-09-10 manuscript.Rmd
updates to western and qpcr

>>>>

```{r western-data}

Protein levels of RPS6 and UBF increased only after twelve sessions in the training group compared to control (Figure 3A) and stayed elevated after eight days of rest. There were no differences between volume-conditions. The average increase in expression levels over twelve sessions were linear in both and estimated to 4 and 8% per session for RPS6 and UBF, respectively.
